Odonate abundance changes in response to the creation of a flood reservoir in a former fen

### 2020-12-03 manuscript/manuscript.Rmd
README updated with proposal information; tweaks to manuscript
working on Travis CI

```{r, echo=FALSE}
install.packages('plyr')
install.packages('dplyr')
```

@@

The first three main objectives will be answered from the dataset from the original study (Morris, 1991). The final sub-bullet is not meant to be answered with true rigor, but as an interesting way to include citizen science. It is not expected to be comprehensive or a full picture of current Odonate diversity at the study site.

@@

```{r, echo=FALSE}
library('plyr')
library('dplyr')

@@

```{r, echo=FALSE,}

@@

```{r, echo=TRUE}
fitTotal <- lm(abunYearsSums$total_abundance ~ abunYearsSums$year)

@@

```{r, echo=FALSE}
library('plyr')
library('dplyr')

@@

```{r, echo=FALSE, fig.cap="Figure 4. Number of species in each year of the study period. Note that this is not a comprehensive list of all Odonates at the site, this will be addressed in the discussion."}
# I want to know how many species there are in a given year, subsetting using the which function and finding the length of that subset
# I will save each as with a corresponding year identifier because I have not yet decided what format I want them all in (dataframe, table, etc.)

>>>>

```{r 1, echo=FALSE}
install.packages('plyr')
install.packages('dplyr')
```

@@

The first three main objectives will be answered from the dataset from the original study (Morris, 1991). The final sub-bullet is not meant to be answered with true rigor and was not an original objective proposed, but is an interesting way to include citizen science. It is not expected to be comprehensive or a full picture of current Odonate diversity at the study site.

@@

```{r 2, echo=FALSE}
library('plyr')
library('dplyr')

@@

```{r 3, echo=FALSE,}

@@

```{r 4, echo=TRUE}
fitTotal <- lm(abunYearsSums$total_abundance ~ abunYearsSums$year)

@@

```{r 5, echo=FALSE}
library('plyr')
library('dplyr')

@@

```{r 6, echo=FALSE, fig.cap="Figure 4. Number of species in each year of the study period. Note that this is not a comprehensive list of all Odonates at the site, this will be addressed in the discussion."}
# I want to know how many species there are in a given year, subsetting using the which function and finding the length of that subset
# I will save each as with a corresponding year identifier because I have not yet decided what format I want them all in (dataframe, table, etc.)
